Fractional Types

### 2016-12-19 typespp.tex
fig:cong
Circuits for name and coname
Some more on name and coname

>>>>

\subsection{\texttt{name} and \texttt{coname}}

Given a \textrm{/-combinator} $p : \#c \leftrightblackspoon \#d$ which is a
morphism in the compact closed category, we can build circuits that construct
the \texttt{name} $\ulcorner{p}\urcorner$ and \texttt{coname}
$\llcorner{p}\lrcorner$ of $p$. These are shown in figure~\ref{fig:name-coname}.

\begin{figure}[ht]
  \begin{subfigure}{.5\textwidth}
    \centering
    \begin{tikzpicture}[scale=0.9,every node/.style={scale=0.7},highlight/.style={line width=4pt,orange!70}]
      \path (-1.1,1) edge node[above] {\footnotesize{${\textsf{[\#id,id]}}$}} (0,1);

      \draw (0,0) -- (1,0) -- (1,2) -- (0,2) -- cycle;
      \node at (0.5,1) {\footnotesize{$\eta -$}};

      \path [highlight] (1,1.75) edge node[above] {} (2,1.75);
      \path (1,1.75) edge node[above] {\footnotesize{$1/\textsf{\#c}$}} (2,1.75);
      \path [highlight] (1,0.25) edge node[above] {} (2,0.25);
      \path (1,0.25) edge node[above] {\footnotesize{${\textsf{\#c}}$}} (2,0.25);
      \draw[dashed] (1.25,1.75) -- (1.25,0.25);

      \draw (2,0) -- (3,0) -- (3,2) -- (2,2) -- cycle;
      \node at (2.5,1) {\footnotesize{$\texttt{cong}$}};

      \path (3,1.75) edge node[above] {\footnotesize{$1/\textsf{\#c}$}} (4,1.75);
      \path (3,0.25) edge node[above] {\footnotesize{${\textsf{\#d}}$}} (4,0.25);

      \path (2.5,0) edge node[left] {\footnotesize{$p : \#c \leftrightblackspoon \#d$}} (2.5,-0.5);
    \end{tikzpicture}
  \end{subfigure}
  \begin{subfigure}{.5\textwidth}
    \centering
    \begin{tikzpicture}[scale=0.9,every node/.style={scale=0.7},highlight/.style={line width=4pt,orange!70}]

      \path (-1.1,1.75) edge node[above] {\footnotesize{$1/\textsf{\#c}$}} (0,1.75);
      \path (-1.1,0.25) edge node[above] {\footnotesize{${\textsf{\#d}}$}} (0,0.25);

      \draw (0,0) -- (1,0) -- (1,2) -- (0,2) -- cycle;
      \node at (0.5,1) {\footnotesize{\texttt{cong}}};

      \path (0.5,0) edge node[right] {\footnotesize{$p : \#c \leftrightblackspoon \#d$}} (0.5,-0.5);

      \path [highlight] (1,1.75) edge node[above] {} (2,1.75);
      \path (1,1.75) edge node[above] {\footnotesize{$1/\textsf{\#c}$}} (2,1.75);
      \path [highlight] (1,0.25) edge node[above] {} (2,0.25);
      \path (1,0.25) edge node[above] {\footnotesize{${\textsf{\#c}}$}} (2,0.25);
      \draw[dashed] (1.75,1.75) -- (1.75,0.25);

      \draw (2,0) -- (3,0) -- (3,2) -- (2,2) -- cycle;
      \node at (2.5,1) {\footnotesize{$\epsilon +$}};

      \path (3,1) edge node[above] {\footnotesize{${\textsf{[\#id,id]}}$}} (4,1);
    \end{tikzpicture}
  \end{subfigure}
  \caption{\label{fig:name-coname} \texttt{name} and \texttt{coname}}
\end{figure}
